He Said What Now?!: Predicting Interest in the Term *China Virus* by State

### 2020-05-06 Final-Draft.Rmd
final-Draft
Update Final-Draft.Rmd

### 5.3a
```{r, echo=FALSE, warning=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
set.seed(454)
pred_FL_RM <- posterior_predict(
  RM_model,
  newdata = new_FL)

pred_FL_RM <- data.frame(y_new = pred_FL_RM[-1])

ggplot(pred_FL_RM, aes(x=y_new))+geom_density()+theme_minimal()

@@

After creating predictions for all the states, we wanted to focus on just one state. That said, we looked at Florida and created future "China Virus" interest predictions for it using each of our models. Our first model, predicts "'China Virus" interest for Florida on Day 7, with the positive rate being 11% and assumes the percentage of white residents is to be 5%. Model 1 predicts the mean interest to be 45.27%, however, as one could see from the above visualization the interest could vary greatly, but there is a higher chance for it to be between 20% - 80%.

### 5.3b
```{r, echo=FALSE, warning=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple") 
set.seed(454)
pred_FL_NR <- posterior_predict(
  NR_model,
  newdata = new_FL)

@@

ggplot(pred_FL_NR, aes(x=y_new))+geom_density()+theme_minimal()

@@

### 5.3c
```{r, echo=FALSE, warning=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_3 <- posterior_predict(
  model_3,
  newdata = new_FL)

@@

ggplot(pred_FL_3, aes(x=y_new))+geom_density()+theme_minimal()

@@

### 5.3d
```{r, echo=FALSE, warning=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_complex <- posterior_predict(
  complexmod,
  newdata = new_FL)

@@

ggplot(pred_FL_complex, aes(x=y_new))+geom_density()+theme_minimal()

>>>>

### 5.3a
```{r, echo=FALSE, warning=FALSE, include=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658) 
set.seed(454)
pred_FL_RM <- posterior_predict(
  RM_model,
  newdata = new_FL)

pred_FL_RM <- data.frame(y_new = pred_FL_RM[-1])
```

```{r echo=FALSE, warning=FALSE}
ggplot(pred_FL_RM, aes(x=y_new))+geom_density()+theme_minimal()

@@

After creating predictions for all the states, we wanted to focus on just one state. That said, we looked at Florida and created future "China Virus" interest predictions for it using each of our models. Our first model, predicts "'China Virus" interest for Florida on Day 7, with the amount of positive cases being 658 and assumes the percentage of white residents is to be 5%. Model 1 predicts the mean interest to be 45.27%, however, as one could see from the above visualization the interest could vary greatly, but there is a higher chance for it to be between 20% - 80%.

### 5.3b

```{r, echo=FALSE, warning=FALSE, include=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple") 
set.seed(454)
pred_FL_NR <- posterior_predict(
  NR_model,
  newdata = new_FL)

@@

```{r echo=FALSE, warning=FALSE}
ggplot(pred_FL_NR, aes(x=y_new))+geom_density()+theme_minimal()

@@

### 5.3c
```{r, echo=FALSE, warning=FALSE, include=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_3 <- posterior_predict(
  model_3,
  newdata = new_FL)

@@

```{r echo=FALSE, warning=FALSE}
ggplot(pred_FL_3, aes(x=y_new))+geom_density()+theme_minimal()

@@

### 5.3d
```{r, echo=FALSE, warning=FALSE, include=FALSE}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive = 658, StateColor="purple")
set.seed(454)
pred_FL_complex <- posterior_predict(
  complexmod,
  newdata = new_FL)

@@

```{r echo=FALSE, warning=FALSE}
ggplot(pred_FL_complex, aes(x=y_new))+geom_density()+theme_minimal()
